Relative Stable Maps in Genus One via Radial Alignments

### 2017-12-16 genus-one-relative-maps.tex
More on setting up notation for blowup

\section{Relative space equals closure of the nice locus}
Have to show that given a relative map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.

@@

Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$. The picture is:

@@

>>>>

\section{Relative space equals closure of the nice locus}
Since the log structures only come into play when the source curve is reducible, it follows that the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting. In particular, it is irreducible.

We now want to show that the relative space in the radially aligned setting is equal to the closure of the nice locus; irreducibility follows immediately. One direction is clear: [WHY?]

It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.

@@

Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$. Finally, suppose that $f$ is not constant on $C_0$. The picture is:

@@

Fix $i =1,\ldots,k$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
\begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}
